\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Coby Benveniste}}\\
	Tel Aviv-Yafo, Israel $\cdot$ coby.benveniste@gmail.com $\cdot$ +972 58 681 8698 $\cdot$ https://cobybenveniste.com\\
\end{center}



%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{OpenWeb (Formerly Spot.IM)} \hfill Tel Aviv-Yafo, Israel\\
\textit{Backend Engineer, Tech Lead, Staff Engineer} \hfill July 2018 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as the senior engineer on the Engineering team at a social engagement platform company.
	\item Developed new services in Ruby, Elixir, and Golang, and helped design the 2.0 architecture of the company utilizing event sourcing designs.
	\item Maintained all legacy services of the company, and led the rewrites of various legacy components into the brand new architecture.
	\item Lead a team of developers in developing and designing the OpenWeb Moderation 2.0 platform, which handles ingesting, tagging, and moderating all of the user generated content of the platform at high scale, with a focus on speed, reliability, and efficiency.
	\item Currently, leading the Labs efforts on the Backend of OpenWeb, working as a \textquotedbl{}Special Forces Engineer\textquotedbl{} to handle highly advanced projects in short timeframes, helping push the technology of the OpenWeb Backend Infrastructure to new levels.
\end{itemize}
\textbf{Signals Analytics} \hfill Netanya, Israel\\
\textit{Software Developer, Data Scientist, Tableau Specialist} \hfill January 2016 - April 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as a Software Developer and Tableau Expert for a big data analytics company.
	\item Changed many paradigms in the company by creating new tools and updating old ones to work much more efficiently.
	\item Developed and maintained a tool for unstructured text classification based on rules specified by analysts, now used in all projects in the company.
	\item Developed innovative models for extracting insights from big data in various industries.
	\item Became the point person on all Tableau related work and optimizations in the company.
\end{itemize}
\textbf{Jamestown, L.P.} \hfill Atlanta, GA\\
\textit{Software Developer} \hfill September 2015 - December 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as an Independent Software Developer for a realty investments company.
	\item Developed a system for automation of tax reporting to the federal government.
\end{itemize}
\textbf{Leapfrog Services, Inc.} \hfill Atlanta, GA\\
\textit{Software Developer} \hfill June 2014 - September 2015\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Worked as an In-House Software Developer creating internal tools for an IT services company.
	\item Developed a scheduling tool for use by the Field Services department to schedule onsite visits by engineers.
	\item Developed a price calculator for use by the Commercial Department to onboard new clients and give price estimates.
	\item Developed various proof-of-concept projects for automation, DevOps, and reporting.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages (experienced):        & Go, Elixir, Ruby, SQL                                  \\
	Programming Languages (limited experience): & Python, TypeScript, C\#                                \\
	Applications (experienced):                 & Git, AWS, Docker, Kubernetes, Kafka, RabbitMQ, Tableau \\
	Databases (experienced):                    & MySQL, ElasticSearch, Redis                            \\
	Operating Systems (experienced):            & MacOS, Windows, Various Linux Flavors                  \\
\end{tabular}
\vspace{2mm}

\header{Recent Selected Projects}
{\textbf{OpenWeb Moderation 2.0}} {\sl Go, MySQL, Redis, Kubernetes, SQS, Kafka} \hfill https://bit.ly/2FM0sRi\\
A platform for ingesting, tagging, and moderating millions of pieces of user generated content at high scale with a focus on speed, reliability, and efficiency.\\
\vspace*{2mm}
{\textbf{OpenWeb Import Infrastructure}} {\sl Go, Redis, SQS, Kafka} \\
An infrastructure for importing terabytes of data from external partners at high speed.\\
\vspace*{2mm}
{\textbf{Starship Web Server}} {\sl Elixir} \hfill https://github.com/probably-not/starship\\
A reactor style web server built from the ground up in pure Elixir.\\
\vspace*{2mm}



\ 
\end{document}
